Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-06 WSSSPE3/report/WSSSPE3_review.tex
add Mike Hildreth's talk

\item \textbf{Mike Hildreth, Jarek Nabrzyski, Da Huo, Peter Ivie, Haiyan Meng,
Douglas Thain and Charles Vardeman: \textit{Data And Software Preservation for Open
Science (DASPOS)}}

>>>>

\item \textbf{Mike Hildreth, Jarek Nabrzyski, Da Huo, Peter Ivie, Haiyan Meng,
Douglas Thain and Charles Vardeman: \textit{Data And Software Preservation for Open
Science (DASPOS)}}
DASPOS is an NSF-funded multi-disciplinary effort, with main host at Notre
Dame, Chicago, and links the HEP effort to Bioligy, Astrophysics, Digital
Curation, and other disciplines. It includes physicists, digital librarians, as
well as computer scientists, and aims to achieve some commonality across
disciplines. Examples are meta-data descriptions of archived data,
computational descriptions, descriptions of how data was processed, but also
includes questions like whether computation replication can be automated, of
what the impact of access policies on the preservation infrastructure is. One
of the products of this effort is a suite of tools that hels with this
preservation, and the questions was posed wether that software itself is
sustainable. Points that were brought up include the need for a user community
depending on a given software, and the need to provide added value for its
users. An important aspect to achieve this to plan to work with the user
community from the start, and to budget that way. For the specific example of
the preservation software this means that besides adding value to the
community, it needs to be transparent to their workflow, i.e., not requiring
additional effort to preserve ``research objects''.
